\cleardoublepage
\phantomsection
\thispagestyle{myheadings}
\renewcommand\thefigure{\arabic{figure}}
\markright{REFERENCES}
\pagestyle{myheadings}
\addcontentsline{toc}{chapter}{References}
\chapter*{References}
\begin{thebibliography}{99}

%\nocite{*}
%\bibitem{Vance} I. A. W. Vance, \emph{Miniature Pager with Novel Receiver On-a-Chip}, Vehicular Technology Conference, 1982. IEEE V. 32, p. 243 - 245, reperibile su \url{http://ieeexplore.ieee.org/iel5/10801/34060/01623025.pdf?arnumber=1623025}.

\bibitem{BalanisAT} C. A. Balanis, \emph{Antenna Theory, Analysis and Design}, $2^\mrm{nd}$ ed., John Wiley \& Sons Inc., 1997.

\bibitem{StutzmanThieleATD} W. L. Stutzman, G. A. Thiele, \emph{Antenna Theory and Design}, John Wiley \& Sons Inc., 1981.

\bibitem{MilliganMAD} T. A. Milligan, \emph{Modern Antenna Design}, $2^\mathrm{nd}$ ed., IEEE Press, Wiley-Interscience, 2005.

\bibitem{SelleriETA} S. Selleri, \emph{Elementi di Teoria degli Array}, Pitagora Editrice Bologna, 2001.

\bibitem{MaillouxPAAH} R. J. Mailloux, \emph{Phased Array Antenna Handbook}, $2^\mrm{nd}$ ed.,  Artech House Inc., 2005.

\bibitem{ZooghbySAE} A. E. Zooghby, \emph{Smart Antenna Engineering}, Mobile Comunications series,  Artech House Inc., 2005.

\bibitem{RothwellCloudE} E. J. Rothwell, M. J. Cloud, \emph{Electromagnetics}, CRC Press LLC, 2001.

\bibitem{OrfanidisEWA} S. J. Orfanidis, \emph{Electromagnetic Waves and Antennas}, Rutgers University, 2008, available at \url{www.ece.rutgers.edu/~orfanidi/ewa}.

\bibitem{StrattonET} J. A. Stratton, \emph{Electromagnetic Theory}, McGraw-Hill Book Compagny Inc., 1941.

\bibitem{VBladelEF} J. G. Van Bladel, \emph{Electromagnetic Fields}, $2^\mathrm{nd}$ ed., IEEE Press, Wiley-Interscience, 2007.

\bibitem{VBladelSEFS} J. G. Van Bladel, \emph{Singular Electromagnetic Fields and Sources}, Oxford University Press, 1991.

\bibitem{BondesonRylanderIngelstroemCE} A. Bondeson, T. Rylander, P. Ingelstr\"{o}m, \emph{Computational Electromagnetics}, Springer, 2005

\bibitem{ThomeeGFEMP} V. Thom\'{e}e , \emph{Galerkin Finite Element Methods for Parabolic Problems}, $2^\mathrm{nd}$ ed., Springer, 2006.

%\bibitem{ChenXuPGIPGMSKIE} Z. Chen, Y. Xu, \emph{The Petrov-Galerkin and Iterated Petrov-Galerkin Method for Second-Kind Integral Equations}, SIAM Journal on Numerical Analysis, Vol. 35, No. 1, pp. 406-434, Feb. 1998, available at \url{http://www.jstor.org/pss/2587110}.

\bibitem{ChatterjeeIPOD} A. Chatterjee, \emph{Introduction to the Proper Orthogonal Decomposition}, Current Science, Vol. 78, No. 7, 10 April 2000.

\bibitem{HalmosMT} P. R. Halmos, \emph{Measure Theory}, Sringer-Verlag, 2000.

\bibitem{RudinFA} W. Rudin, \emph{Functional Analysis}, McGraw-Hill Book Compagny Inc., 1973.

\bibitem{GiaquintaModicaMA}  M. Giaquinta, G. Modica, \emph{Mathematical Analysis, Linear and Metric Structures and Continuity}, Birkh\"{a}user, 2007.

\bibitem{SaadIMSLS} Y. Saad, \emph{Iterative Methods for Sparse Linear Systems}, University of Minnesota, $2^\mathrm{nd}$ ed., 2000, available at \url{http://www-users.cs.umn.edu/~saad/}.

\bibitem{Orfanidis} S. J. Orfanidis, \emph{SVD, PCA, KLT, CCA, and All That}, Rutgers University, 2007, available at \url{www.ece.rutgers.edu/~orfanidi/ece525/svd.pdf}.

\bibitem{TrefethenBauNLA} L. N. Trefethen, D. Bau, \emph{Numerical Linear Algebra}, SIAM, 1997.

\bibitem{AntoulasALSDS} A. C. Antoulas, \emph{Approximation of Large-Scale Dynamical Systems}, SIAM, Advances in Design and Control, 2005.


\bibitem{HuynPateraRBStress} D.B.P. Huynh, A.T Pater, \emph{Reduced basis approximation and a posteriori error estimates for stress intensity factors}, International Journal for Numerical Methods in Engineering, 72 (10): 1219-1259, 2007, available at \url{http://augustine.mit.edu/methodology/papers/atpIJNMEpreprint.pdf}.

\bibitem{PateraBarraultEIMRB} M. Barrault, Y. Maday, N. C. Nguyen, A. T. Patera, \emph{An \quotes{empirical interpolation} method: application to efficient reduced-basis discretization of partial differential equations}, Acad\'{e}mie des Sciences, Elsevier SAS, 2004, available at \url{http://augustine.mit.edu/methodology/papers/atpCRAS2004.pdf}.

\bibitem{PateraRozzaRBPEEA} G. Rozza, D.B.P. Huynh, A.T. Patera \emph{ Reduced Basis Approximation and a Posteriori Error Estimation for Affinely Parametrized Elliptic Coercive Partial Differential Equations}, Archives of Computational Methods in Engineering, vol. 15, num. 3, pp. 229-275, 2008, available at \url{http://www.springerlink.com/content/vur203773327381j/}.

\bibitem{GuarnieriSelleriFEDD} G. Guarnieri, G. Pelosi, L. Rossi and S. Selleri \emph{FE-DD Based Permittivity Tolerance Analysis in Microwave Waveguide Filters} COMPEL, Vol. 27 No. 6, pp. 1236-1248, 2008, available at \url{http://dx.doi.org/10.1108/03321640810905729}.

\bibitem{SelleriEdlingerDDMOR} S. Selleri, O. Farle, G. Guarnieri, M. Losch, G. Pelosi,  R. Dyczij-Edlinger, \emph{A Combined Domain Decomposition - Model Order Reduction Technique for Fast Finite Element Parametric Sweeps} IEEE Antennas and Propagation Society International Symposium, 2008, available at \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4619422}.

\bibitem{BertazziGhioneMOR} F. Bertazzi, O. A. Peverini, M. Goano, G. Ghione, R. Orta, R. Tascone, \emph{A Fast Reduced-Order Model for the Full-Wave FEM Analysis of Lossy Inhomogeneous Anisotropic Waveguides}, IEEE Transactions on Microwave Theory and Techniques, Vol. 50, No. 9, Sept 2002, available at \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=1028951}.


\bibitem{JinFEME} J. Jin, \emph{The Finite Element Method in Electromagnetics}, John Wiley \& Sons Inc, 2002.

\bibitem{SchneiderMDMOR} A. Schneider, \emph{Matrix decomposition based approaches for model order reduction of linear systems with a large number of terminals}, Diploma thesis, Chemnitz University of Technology, Department of Mathematics, April 2008, available at \url{http://www-user.tu-chemnitz.de/~schnea/Data/diplomarbeit.pdf}.

\bibitem{RileyHobsonBenceMMPE} K.F. Riley, M.P. Hobson, S. J. Bence, \emph{Mathematical Methods for Physics and Engineering}, Cambridge University Press, 2006.

\bibitem{BrighamFFT} E. O. Brigham, \emph{The Fast Fourier Transform}, Prentice-Hall, 1974.

\bibitem{PelosiCoccioliSelleriQFEEF} G. Pelosi, R. Coccioli, S. Selleri, \emph{Quick Finite Elements for Electromagnetic Fields}, Artech House, 1998.

\bibitem{FarleMORFE} O. Farle, \emph{Ordnungsreduktionsverfahren f\"{u}r die Finite-Elemente-Simulation parameterabh\"{a}ngiger passiver Mikrowellenstrukturen}, Universit\"{a}t des Saarlandes, Doctorate Thesis, 2007.

\bibitem{MonkFEME} P. Monk, \emph{Finite Element Methods for Maxwell's Equations}, Oxford University Press, 2003.

\bibitem{ZhuCangellarisMFEMEFM} Y. Zhu, A. C. Cangellaris, \emph{Multigrid Finite Element Methods for Electromagnetic Field Modeling}, IEEE Press, Wiley-InterScience, 2006.

\bibitem{BrackenSunCendesSDom} J. E. Bracken, D. K. Sun, Z. J. Cendes, \emph{S-Domain Methods for Simultaneous Time and Frequency Characterization of Electromagnetic Devices} IEEE Transactions on Microwave Theory and Techniques, Vol. 46, No. 9, September 1998, available at \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=00709471}.

\bibitem{LedgerPerairePESSRIWA} P.D. Ledger, J. Peraire, K. Morgan, O. Hassan, N.P. Weatherill, \emph{Parameterised Electromagnetic Scattering Solutions for a Range of Incident Wave Angles}, Elvesier, 2004, available at \url{http://dx.doi.org/10.1016/j.cma.2004.01.032}.

\bibitem{MonkN2F} P. Monk, \emph{The Near Field to Far Field Transformation}, COMPEL, The International Journal for Computation and Mathematics in Electrical and Electronic Engineering, Vol 14, No 1, P. 41-56, 1995, available at \url{http://dx.doi.org/10.1108/eb010137}.

\bibitem{IhlenburgBabuskaDAEE} F. Ihlenburg, I. Babu\v{s}ka, \emph{Dispersion Analysis and Error Estimation of Galerkin Finite Element Methods for the Helmholtz Equation}, International Journal for Numerical Methods in Engineering, Vol 38, P. 3745-3774, 1995.

\bibitem{ChioSchaubertPSDWB} T.H. Chio, D.H. Schaubert, \emph{Parameter Study and Design of Wide-Band Widescan Dual-Polarized Tapered Slot Antenna Arrays}, IEEE Transactions on Antennas and Propagation, vol. 48, no. 6, pp. 879-886, June 2000.



\end{thebibliography}
